### 2021-06-11 paper/results.tex
Outline for rest.
Cleaned up: \color{red} -> \comment[id=J].

\textcolor{red}{The results can be found in `figures/results`. This includes both figures
and tables for lookup of numbers and summary tables.}

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
\end{subfigure}
\caption{The Effect of Policies on Observed and Unobserved Cases}
\label{fig:explain_decline}
\figurenotes{\textcolor{red}{\ldots}}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
\end{subfigure}
\caption{The Effect of Different School Scenarios on Observed and Unobserved Cases}
\figurenotes{\textcolor{red}{K: One of the scenarios starts too early. Will be fixed with the next full simulations run.}}
\label{fig:school_scenarios}
\end{figure}

@@

\begin{figure}[ht]
\centering
% \includegraphics[width=\textwidth]{../figures/preliminary_shapley}
\caption{Shapley Values}
\figurenotes{\textcolor{red}{K: These are taken from Tobi's notebook as examples. Numbers
might still change}}
\label{fig:school_scenarios}

\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
  \end{subfigure}%
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
  \end{subfigure}
  \caption{The Effect of Policies on Observed and Unobserved Cases}
  \label{fig:explain_decline}
  \figurenotes{\ldots}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_new_known_case}
  \end{subfigure}%
  \begin{subfigure}{.6\textwidth}
    \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
  \end{subfigure}
  \caption{The Effect of Different School Scenarios on Observed and Unobserved Cases}
  \figurenotes{}
  \label{fig:appdx_school_scenarios}
\end{figure}

@@
